\paragraph\
I take this opportunity with immense pleasure to convey my gratitude to my supervisor, {\bf Ms. Anupama Potluri} who acted as a challenging captain coordinating all of our batch with great patience and invaluable suggestions. They really helped me to complete this task well before the stipulated time. She has always encouraged, supported, corrected and guided me during the project. This project happened to be one of my best journeys through core concepts of Computer Networks. The constant guidance of our supervisor helped me to develop both individually and professionally.\\

I can not get a better opportunity than this to thank profusely my senior {\bf Y. Jaya Lakshmi} with whose hard work my project literally became a cake walk. I would like to thank {\bf Tholoana Masupha} who is also part of this project. I am extreamly thankful to my lab mates {\bf B. Saritha, \bf B.Vishala and  \bf L. Ramprasad } for continuously inputting me with their valuable suggestions and being a source of encouragement at all possible times.  I would also like to thank the developers of {\bf ns2} for providing such a wonderful and robust software to work along with detailed documentation.\\

I am extremely grateful to our Head of Department, {\bf Prof. Arun Agarwal}, for providing excellent computing facilities and such a nice atmosphere for doing my project. I convey my heartfelt thanks to {\bf AI Lab staff} for their help in completing the project work successfully. \\

Last but not the least, I would like to express my heartful wishes to my beloved parents and my dear friends whose gracious solicitude helped me to complete this project successfully.  


\indent \indent \indent \indent \indent \indent \indent \indent \indent \indent \indent \indent \indent \indent \indent \indent \indent {\bf Sravanthi Bhavanam}